Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-24 paper.qmd
Updated Figure 4b

two_curvy_proj_tsne_first_model1 <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.6, 0.6), 
    axis_text_size = 2, 
    is_category = FALSE) +
  interior_annotation(label = "b", cex = 1.2) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

two_curvy_proj_tsne_first_model1_coloured <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2,
      colour = cluster)) +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  scale_colour_manual(values = c("#FFFFC8", "#FFFAC0", "#FEF2B3", "#FCE9A3",
                                 "#FADE8F", "#F9D378", "#F8C65D", "#F6B938",
                                 "#F5AA00", "#F49B00", "#F28A00", "#F07800",
                                 "#ED6400", "#EA4D00", "#DE3900", "#CD2A00",
                                 "#BB1B00", "#A70C00", "#93001C", "#7D0025")) +
  xlim(c(-0.6, 0.6)) +
  ylim(c(-0.6, 0.6)) +
  interior_annotation(label = "c", cex = 1.5) +
  theme(aspect.ratio = 1,
        legend.position = "none")

>>>>

two_curvy_proj_tsne_first_model1 <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.75, 0.75), 
    axis_text_size = 2, 
    is_category = FALSE) +
  interior_annotation(label = "b", cex = 1.2) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

two_curvy_proj_tsne_first_model1_coloured <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2,
      colour = cluster)) +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  scale_colour_manual(values = c("#FFFFC8", "#FFFAC0", "#FEF2B3", "#FCE9A3",
                                 "#FADE8F", "#F9D378", "#F8C65D", "#F6B938",
                                 "#F5AA00", "#F49B00", "#F28A00", "#F07800",
                                 "#ED6400", "#EA4D00", "#DE3900", "#CD2A00",
                                 "#BB1B00", "#A70C00", "#93001C", "#7D0025")) +
  xlim(c(-0.75, 0.75)) +
  ylim(c(-0.75, 0.75)) +
  interior_annotation(label = "c", cex = 1.5) +
  theme(aspect.ratio = 1,
        legend.position = "none")
